---
title: "Dynamic report"
output:
  html_document:
    theme: united
    highlight: tango
  

params:
  Filt: NA
  Area: NA
  Geo: NA
  ST: NA
  Analy: NA
  Group: NA

---
\singlespacing
## Analyis of Issues `r params$Filt$issueA` and `r params$Filt$issueB`
### The flags you selected are `r params$Filt$Level_1` and `r params$Filt$Level_2`


### Filters
* **Race:**  **`r params$Filt$Race`** 
* **Age Range:** **`r params$Filt$Age[1]`** **to** **`r params$Filt$Age[2]`** 
* **Gender:** **`r params$Filt$Gender`**

*** 

`r if(params$Filt$ST_Eval){"# Spread Tables {.tabset}"}` 

`r if(params$Filt$ST_Eval){"## Total Overlap"}`


```{r, echo=FALSE, eval=params$Filt$ST_Eval}
#library(VennDiagram)
#grid.draw(params$venn)
params$ST$Partisan

```


`r if(params$Filt$ST_Eval){"##  Race - Age - Partisanship"}`
```{r echo=FALSE, eval=params$Filt$ST_Eval}
params$ST$Age
params$ST$Race
```


`r if(params$Filt$Geo_Eval){"# Geographic Data {.tabset}"}` 

`r if(params$Filt$Geo_Eval){"## Map & Graphs"}` 

```{r out.width=c("100%"), echo=FALSE, eval=params$Filt$Geo_Eval}
library('leaflet')
params$Geo$Mappy
```

`r if(params$Filt$Geo_Eval){"## Geo Table"}` 
```{r echo=FALSE, eval=params$Filt$Geo_Eval}
params$Geo$DT
```

* *Total Voters: Total number of voters in the zip code* 
* *Selected Voters: Number of Voters with both flags*
* *Concentration: Percent of total voters with both flags*
***

***

`r if(params$Filt$Analy_Eval){"# Analytics {.tabset}"}`

```{r, echo=FALSE, results='asis', eval=params$Filt$Analy_Eval}

cat("## Conditional Probabilities")

```

```{r, echo=FALSE, eval=params$Filt$Analy_Eval}
params$Analy$Prob_BA
params$Analy$Prob_AB
```

```{r, echo=FALSE, results='asis', eval=params$Filt$Analy_Eval}

cat("## Shared with Both Similatiry")

```

```{r, echo=FALSE, eval=params$Filt$Analy_Eval, out.width=c('50%', '50%')}
params$Analy$Most_Shared
```

```{r, echo=FALSE, results='asis', eval=params$Filt$Analy_Eval}

cat("## One Way Similatiry")

```


```{r, echo=FALSE, eval=params$Filt$Analy_Eval, out.width=c('50%', '50%')}
params$Analy$First_Flag
params$Analy$Second_Flag
```


`r if(params$Filt$Group_Eval){"# Group Comparisions {.tabset}"}`
`r if(params$Filt$Group_Eval){"## Group Filter Selections {.tabset}"}`
```{r, echo=FALSE, eval=params$Filt$Group_Eval, out.width=c('50%', '50%'), cache=TRUE}

G1_Race_Lab<-paste(params$Group$G1_Race, collapse = " and ")
G1_Age_Lab<-paste(params$Group$G1_Age, collapse = " to ")
G1_labels <- sprintf(
    "<strong>Group 1:</strong><br/>Race: %s<br/>Age: %s<br/>Gender: %s <br/>
    <br/>Income range: %s<br/>Included Elections: %s<br/>Excluded Elections %s",
    G1_Race_Lab, G1_Age_Lab, params$Group$G1_Gender, 
    params$Group$G1_Income_Range, params$Group$G1_Elections, params$Group$G1_No_Elections
  ) %>% lapply(htmltools::HTML)

G2_Race_Lab<-paste(params$Group$G2_Race, collapse = " and ")
G2_Age_Lab<-paste(params$Group$G2_Age, collapse = " to ")
G2_labels <- sprintf(
    "<strong>Group 2:</strong><br/>Race: %s<br/>Age: %s<br/>Gender: %s <br/>
    <br/>Income range: %s<br/>Included Elections: %s<br/>Excluded Elections %s",
    G2_Race_Lab, G2_Age_Lab, params$Group$G2_Gender, 
    params$Group$G2_Income_Range, params$Group$G2_Elections, params$Group$G2_No_Elections
  ) %>% lapply(htmltools::HTML)


```



```{r, echo=FALSE, results='asis', eval=params$Filt$Group_Eval}

cat(':::: {style="display: grid; grid-template-columns: 1fr 1fr; grid-column-gap: 10px;"}')
```
::: {}

```{r, echo=FALSE, eval=params$Filt$Group_Eval}
htmltools::knit_print.html(G1_labels)
```

:::


::: {}
```{r, echo=FALSE, eval=params$Filt$Group_Eval}
htmltools::knit_print.html(G2_labels)
```

:::

::::

`r if(params$Filt$Group_Eval){"## Most Common Flags {.tabset}"}`

```{r, echo=FALSE, eval=params$Filt$Group_Eval, out.width=c('50%', '50%')}
params$Group$G1_MC
params$Group$G2_MC
```



`r if(params$Filt$Group_Eval){"## Partisanship {.tabset}"}`
```{r, echo=FALSE, eval=params$Filt$Group_Eval, out.width=c('50%', '50%')}
params$Group$G1_Part
params$Group$G2_Part
```

`r if(params$Filt$Group_Eval){"## Most & Least Agreed {.tabset}"}`
```{r, echo=FALSE, eval=params$Filt$Group_Eval, out.width=c('50%', '50%')}
params$Group$Chi_MS
params$Group$Chi_LS
```
***

`r if(params$Filt$Analy_Eval){"# Area Analysis {.tabset}"}`
`r if(params$Filt$Analy_Eval){"## Sankey {.tabset}"}`

```{r, echo=FALSE, eval=params$Filt$Analy_Eval, fig.dim=c(10,6)}
Areass<-paste(params$Area$Areas, collapse = ", ") 

  sprintf("<br/>Selected: %s<br/>", Areass) %>% 
  htmltools::HTML() %>% 
  htmltools::knit_print.html()

params$Area$sankey
```

`r if(params$Filt$Analy_Eval){"## Race & Age {.tabset}"}`
```{r, echo=FALSE, eval=params$Filt$Analy_Eval, fig.dim=c(10,4)}
Areass<-paste(params$Area$Areas, collapse = ", ") 

  sprintf("<br/>Selected: %s<br/>", Areass) %>% 
  htmltools::HTML() %>% 
  htmltools::knit_print.html()

params$Area$barstack
```

`r if(params$Filt$Analy_Eval){"## Political Party {.tabset}"}`
```{r, echo=FALSE, eval=params$Filt$Analy_Eval}
Areass<-paste(params$Area$Areas, collapse = ", ") 

  sprintf("<br/>Selected: %s<br/>", Areass) %>% 
  htmltools::HTML() %>% 
  htmltools::knit_print.html()

params$Area$byparty
```
